D-Hammer: Efficient Equational Reasoning for Labelled Dirac Notation

### 2025-01-31 06related_conclusion.tex
minor
related work on tree automata

>>>>

Automata-based approaches has also been successfully applied for reasoning about quantum circuit~\cite{AutoQ_pldi_2023}. Instead of representing a set of  $n$-qubit states in exponential size, \cite{AutoQ_pldi_2023} encode it as (finite) tree automata with much less (often $\mathit{poly}(n)$) transitions.  They further established transformers to implement the semantics of quantum gates over this representation, providing better scalability compared to other approaches. It is developed as a practical tool \textsc{autoq} with the capabilities for symbolic reasoning~\cite{AutoQ2023}. More recently, \cite{AutoQ_popl2025} further explore level-synchronized tree automata to encoding state, a promising model for parameterized verification.
